Flexibility of interactions depends on habitat suitability

### 2019-09-01 paper/manuscript.Rmd
Add a couple notes in the discussion

Note that although abundances can inflence wether two species interact we cannot tease t appart because suitability is not necessarily related to abundance. ALthough abundance affects the frequency of the interaction, rather than wether they interacts or not (Donoso)

>>>>

<!-- Note that although abundances can inflence wether two species interact we cannot tease t appart because suitability is not necessarily related to abundance. ALthough abundance affects the frequency of the interaction, rather than wether they interacts or not (Donoso) -->

<!--Mention implications for community assembly? -->
